### 2024-10-17 paper.tex
Initial commit

\documentclass[reprint,amsmath,amssymb,aps,pre,showkeys,showpacs]{revtex4-1}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{bm}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage[export]{adjustbox}

\newcommand{\highlight}[1]{{\color{red}{#1}}} % convinient for revised version

\begin{document}
\preprint{APS/123-QED}

\author{Vasily~Postnicov\textsuperscript{1,3}}
\author{Marina~V.~Karsanina\textsuperscript{1,2}}
\author{Aleksey~Khlyupin\textsuperscript{1,2}}
\author{Kirill~M.~Gerke\textsuperscript{1,2}}
\email{kg@ifz.ru}

\affiliation{\textsuperscript{1}Moscow Institute of Physics and Technology,
  Dolgoprudny, 141701, Russia}
\affiliation{\textsuperscript{2}Schmidt Institute of Physics of the Earth of
  Russian Academy of Sciences, Moscow, 107031, Russia}
\affiliation{\textsuperscript{3}Dokuchaev Soil Science Institute, Moscow, 119017, Russia}

\title{Look, we can do something}

\begin{abstract}
We can do some calculations and tell the world about it.
\end{abstract}
\keywords{Porous space, parameters}

\maketitle

\section{Introduction}
Recently, various numeric parameters were developed to qualify 2D slices of the
porous space or individual pores, including this shit here and that shit
there. In this work we are trying to find a numeric parameter which assesses
quality of pore network extraction from a SEM slice by judging if an individual
pore can be divided into more subpores or not. This work expands the efforts
made by Karsanina et al.\cite{PLoS_ONE} \highlight{Or not Karsanina. Must point
to the Skvortsova's parameter}.

\section{A new pore shape parameter}
We propose a new parameter for shape description which is based on the idea of
numerical assession of bottle necks in pores. For simplicity, we will assume
that our pore is 1-connected. Suppose you have a round pore in the form close to
a disk and another pore in the form of a dumbbell. We want to develop a
parameter which would be close to 1 for the first pore and close to 0 for the
second. For this purpose we want to visit all points which lie on the pore's
boundary and find a pair of points which form a bottle neck and have a small
distance between each other. Obviously, not all pairs of points which are close
to each other form a bottle neck. Namely, on \cref{fig:parameter} points $A$ and
$B$ form a bottle neck and points $A$ and $C$ do not form it. If you choose a
point $O$ which lies outside of the pore and travel along the pore's boundary in
one direction (either clockwise or counter-clockwise), when you arrive at $A$
you will see the point $O$ to your left and when you are in $B$ you will see $O$
to your right (or vice-versa). But if you are at $A$ or $C$ you will see $O$ to
the same side from you. Instead of doing this check for ``bottle-neckness'', we
add a penalty coefficient to the distance between points, namely for a pair of
points $(A, B)$ we calculate the following:
\begin{equation}
  p_{AB} = \rho_{AB} / L_{AB}
  \label{eq:intro}
\end{equation}
where $\rho_{AB}$ is the Euclidean distance between $A$ and $B$ and $L_{AB}$ is
the length of a pore's boundary segment with end points $A$ and $B$ (there are
two such segments, you need to take the segment with minimal length). Suppose
$B$ is a set of all points on the pore's boundary. We define a new pore shape
parameter $p$, called ``\highlight{awesomeness}'', using \ref{eq:intro}:
\begin{equation}
  p = \inf \{p_{AB} \ \forall (A, B) \in B^2\}
\end{equation}
Obviously, it's unlikely that $p$ = $p_{AC}$ because $L_{AC} \approx \rho_{AC}$.
It's easy to see that $0 \le p \le 1$ because $0 \le \rho_{AB} \le L_{AB}$ for
any $A$ and $B$ for a line segment which connects $A$ and $B$ is the shortest
of all other curves which connect those points.
\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{images/parameter.png}
  \caption[]{A dumbbell-like boundary of a pore. Points $A$ and $B$ form a
    bottle neck while points $A$ and $C$ do not. This can seen by a relative
    position of the point $O$ while traversing the boundary
    counter-clockwise. Namely, it's on the left side when crossing $A$ but on
    the right side when crossing $B$. When crossing $A$ and $C$, the relative
    position of $O$ does not change. The parameter $p_{AB}$ is equal to the
    distance between $A$ and $B$ divided by length of the blue contour $L$.}
  \label{fig:parameter}
\end{figure}

\section{Computational algorithm}
\label{seq:alg}
Our algorithm for calculating \highlight{awesomeness} is quite simple. It
assumes that an image of a pore is made with sufficient resolution, so we can
use boundary pixels without any additional processing. The main algorithm
consists of three parts and is shown in \cref{alg:main}.
\begin{algorithm}[H]
  \caption{Algorithm for computation of \highlight{awesomeness} of a pore.}
  \label{alg:main}
  \begin{algorithmic}[1]
    \Procedure{\texttt{awesomeness}}{\texttt{img}}
    \State \texttt{bs $\gets$ boundary(img)}
    \Comment Construct a list of boundary points (\cref{alg:extraction}).
    \State \texttt{\%bs $\gets$ sort(bs)}
    \Comment Sort points as described in \cref{alg:sort}.
    \State \textbf{return} \texttt{pmin(\%bs)}
    \EndProcedure
  \end{algorithmic}
\end{algorithm}

The first step extracts a list of boundary points from an image of a pore, the
second step sorts them in the order descried later and the third and the last
step minimizes $p_{AB}$ parameter for each pair of points $(A, B)$ which lie on
the boundary.

Suppose the boundary is defined by a parameteric equation
\begin{equation*}
  \begin{aligned}
    x &= f(t) \\
    y &= g(t)
  \end{aligned}
\end{equation*}
or, using a shorter notation,
$B = \begin{pmatrix} x_B \\ y_B \end{pmatrix} = \begin{pmatrix} f \\ g \end{pmatrix}(t)$
Suppose, you have two points: $B_1 = \begin{pmatrix} f \\ g \end{pmatrix}(t_1)$
and $B_2 = \begin{pmatrix} f \\ g \end{pmatrix}(t_2)$. The sorting in the step 2
implies that if $t_1 < t_2$, the point $B_1$ must appear before $B_2$ in $bs$.

In the following algorithms we will use a notion of single linked lists (or
simply lists). A list of elements of type $a$ can be defined using the following
data type with two constructors, \texttt{[]} and \texttt{(:)}:
\begin{verbatim}
data List a = [] | a:(List a)
\end{verbatim}
The first constructor creates an empty list and the second attaches an element
of type $a$ to the list of elements of type $a$. Sometimes we will use
conventional functions for working with lists such as \texttt{head},
\texttt{tail}, \texttt{map}, \texttt{foldl} and so on.

The algorithm for boundary extraction is shown in \cref{alg:extraction}.
\begin{algorithm}[H]
  \caption{Algorithm for boundary extraction. Takes an image of a pore and
    returns a list of points (indices) which belong to the boundary. It assumes,
  that pore pixels have a value 1 and background pixels have a value 0.}
  \label{alg:extraction}
  \begin{algorithmic}[1]
    \Procedure{\texttt{boundary}}{\texttt{img}}
    \Procedure{\texttt{boundaryp}}{\texttt{index}}
    \State \textbf{return} true if there are background pixels to the left,
    right, up or down from the pixel with this index, false otherwise.
    \EndProcedure
    \Procedure{\texttt{accumulate}}{\texttt{acc, index}}
    \If{\texttt{img[index] = 1} $\wedge$ \texttt{boundaryp(index)}}
    \State \textbf{return} \texttt{index:acc}
    \Else
    \State \textbf{return} \texttt{acc}
    \EndIf
    \EndProcedure
    \State \textbf{return} \texttt{foldl accumulate [] all\_indices(img)}
    \EndProcedure
  \end{algorithmic}
\end{algorithm}

Sorting the boundary points can be done by ensuring that every two consecutive
points have Chebyshev distance equal to 1. This is done by making a list which
contains some (maybe random) point on the boundary and successive addition
neighbor points (relative to the head of that list) to the list. It may be that
all neighbors must be tried to successfully construct the sorted list.

As a heuristic, we maintain a list of seen neighbors, that is, for every point
added to the sorted list we obtain all its neighbors and add them to a separate
list. When a point is added to the sorted list, it is removed from that
list. Before adding any point we consult this list of neighbors to ensure that
there is no point which is farther than 1 from the point on the head of the
sorted list. If this is not so, we give up with the current sorted list and try
to find another list instead.

The final remark is that in order to find neighbors of a point we either have to
build a metric tree (like BK-tree) or keep one extra bit array to mark boundary
points and provide a way to do quick searches for neighbors of some arbitrary
point. A complete algorithm is \cref{alg:sort} where BK-trees are used.
\begin{algorithm}[H]
  \caption{Algorithm for sorting a list of boundary points.}
  \label{alg:sort}
  \begin{algorithmic}[1]
    \Procedure{\texttt{sort}}{\texttt{points}}
    \State \texttt{start $\gets$ head(points)}
    \State \texttt{tree $\gets$ bk\_tree(tail(points))}
    \Procedure{\texttt{go}}{\texttt{sorted, neighbors, tree}}
    \Comment \texttt{sorted} contains a list of sorted boundary points,
    \texttt{neighbors} is an additional list of seen neighbors, \texttt{tree} is
    a BK-tree of unsorted points.
    \If{\texttt{tree\_empty\_p(tree)}}
    \State \textbf{return} \texttt{sorted}
    \Comment No more unsorted points, we are finished.
    \EndIf
    \State \texttt{last $\gets$ head(sorted)}
    \Procedure{\texttt{check\_dist}}{\texttt{point}}
    \State \textbf{return} \texttt{cheb\_dist(last, point) = 1}
    \EndProcedure
    \If{\texttt{notevery(check\_dist, neighbors)}}
    \State \textbf{return} \texttt{[]}
    \Comment We have failed, try to sort another way
    \EndIf
    \State \texttt{ns $\gets$ bk\_tree\_search(tree, last, 1)}
    \Comment Search all points which have Chebyshev distance to \texttt{last} no
    more than 1.
    \State \texttt{\%neighbors $\gets$ tail(sorted) = [] ? [] : union(neighbors, ns)}
    \Comment If we have only one point in the sorted list, do not keep the
    neighbors.
    \Procedure{\texttt{\%go}}{\texttt{neighbor}}
    \State \texttt{\%sorted $\gets$ neighbor:sorted}
    \State \texttt{\%\%neighbors $\gets$ remove(neighbor, \%neighbors)}
    \State \texttt{\%tree $\gets$ bk\_tree\_remove(tree, neighbor)}
    \State \textbf{return} \texttt{go(\%sorted, \%\%neighbors, \%tree)}
    \EndProcedure
    \State \texttt{sorted $\gets$ map(\%go, ns)}
    \State \textbf{return} The first non-empty list from \texttt{sorted}, if
    any. Otherwise return \texttt{[]}.
    \EndProcedure
    \State \textbf{return} \texttt{go([start], [], tree)}
    \EndProcedure
  \end{algorithmic}
\end{algorithm}

The \cref{alg:sort} serves two purposes: not only it sorts boundary points, it
also checks the boundary for correctness. If boundary points in the unsorted
list do not represent a simple closed curve (like on \cref{fig:good-and-bad}),
\texttt{sort} will return an empty list.
\begin{figure}[tp]
  \centering
  \subfigure[A good boundary]{
    \includegraphics[width=0.4\linewidth]{images/good.png}}
  \subfigure[Points do not represent a simple curve (one point is crossed
    twice)]{
    \includegraphics[width=0.4\linewidth]{images/bad.png}}
  \vskip\baselineskip
  \subfigure[Some points are crossed twice]{
    \includegraphics[width=0.4\linewidth]{images/bad2.png}}
  \subfigure[Points do not represent a closed curve]{
    \includegraphics[width=0.4\linewidth]{images/bad3.png}}
  \caption[]{A good set of boundary points and three examples of inacceptable
    boundary discarded by \texttt{sort}.}
  \label{fig:good-and-bad}
\end{figure}

Finaly, the function \texttt{pmin} is described in \cref{alg:pmin}. This
algorithms assumes that there are enough boundary points in an image. If, for
example, an image is taken with bad resolution (i.e. pores consist only of a few
pixels) some quality improving techniques must be applied first.
\begin{algorithm}[H]
  \caption{The last step of the algorithm for awesomeness: the function \texttt{pmin}.}
  \label{alg:pmin}
  \begin{algorithmic}[1]
    \Procedure{\texttt{pairwise\_distances}}{\texttt{points}}
    \State \textbf{return} \texttt{map(dist, points, tail(points))}
    \Comment Return the Euclidean distance between $i$-th and $i+1$-th
    points. The function \texttt{dist} calculates the distance between two
    points.
    \EndProcedure
    \Procedure{\texttt{perimeter}}{\texttt{points}}
    \State \texttt{p1 $\gets$ foldl((+), 0, pairwise\_distances(points))}
    \State \texttt{p2 $\gets$ dist(head(points), last(points))}
    \State \textbf{return} \texttt{p1 + p2}
    \EndProcedure
    \Procedure{\texttt{minimize\_on\_head}}{\texttt{acc, p, points}}
    \Comment \texttt{acc} is the best (minimal) parameter found so far,
    \texttt{p} is a perimeter of the boundary.
    \Procedure{\texttt{go}}{\texttt{acc, x}}
    \State \texttt{(point, boundary\_dist) $\gets$ x}
    \State \texttt{awesomeness $\gets$ dist(point, head(points)) /
      min(boundary\_dist, p - boundary\_dist)}
    \State \textbf{return} \texttt{min(acc, awesomeness)}
    \EndProcedure
    \State \texttt{ds $\gets$ scanl((+), 0, pairwise\_distances(points))}
    \State \texttt{tmp $\gets$ zip(tail(points), tail(ds))}
    \State \textbf{return} \texttt{foldl(go, acc, tmp)}
    \EndProcedure
    \Procedure{\texttt{pmin}}{\texttt{points}}
    \State \texttt{p $\gets$ perimeter(points)}
    \Procedure{\texttt{go}}{\texttt{acc, points}}
    \State \textbf{return} \texttt{minimize\_on\_head(acc, p, points)}
    \EndProcedure
    \State \textbf{return} \texttt{foldl(go, +infinity, points)}
    \EndProcedure
  \end{algorithmic}
\end{algorithm}
If \texttt{sort} cannot sort boundary points, \texttt{pmin} will return
\texttt{+infinity}.

Although a guaranteed upper bound for awesomeness is 1, it's reachable only for
degenerate shapes in the form of line segments. The biggest value for
non-degenerate shapes is reached for a disk and equals to $2/\pi$.

\section{Results}
We computed \highlight{awesomness} for 4000 synthetically generated images with
dimensions $1000 \times 1000$ pixels (1000 images from 4 different
datasets). The datasets have the following properties:
\begin{itemize}
\item \texttt{normal}: ``Normal'' pores with convexity $0.5-0.8$.
\item \texttt{mnist}: Pores which resemble digits (still being 1-connected).
\item \texttt{thin}: Pores with low convexity ($< 0.5$) which resemble thin
  stripes.
\item \texttt{mostlyconvex}: Pores with convexity close to $1$.
\end{itemize}
Figure \ref{fig:pores} depicts a pore from each dataset.
\begin{figure}
    \centering
  \subfigure[\texttt{normal}]{
    \includegraphics[width=0.4\linewidth]{images/normal.png}}
  \subfigure[\texttt{thin}]{
    \includegraphics[width=0.4\linewidth]{images/thin.png}}
  \vskip\baselineskip
  \subfigure[\texttt{mnist}]{
    \includegraphics[width=0.4\linewidth]{images/mnist.png}}
  \subfigure[\texttt{mostlyconvex}]{
    \includegraphics[width=0.4\linewidth]{images/mostlyconvex.png}}
  \caption[]{One pore from each dataset used for calculation of
    \texttt{awesomeness}.}
  \label{fig:pores}
\end{figure}

\section{Comparison with other parameters}
\highlight{CEA vs CER}.

\bibliography{paper}
\end{document}

### 2024-10-18 scripts/plot-ae.py
Add some scripts and images

@@ -1,0 +1,32 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+import pandas as pd
+import sqlite3
+
+with sqlite3.connect('glyphs.db') as db:
+    general = pd.read_sql_query('select * from pores where lfer > 0.9', db)
+
+shit = pd.read_csv('score.csv')
+data = general.merge(shit, on = 'label', how = 'inner', validate = "1:1")
+
+normal = data.query('name == "normal/"')
+thin = data.query('name == "thin/"')
+mnist = data.query('name == "mnist/"')
+mostlyconvex = data.query('name == "mostlyconvex/"')
+
+f = lambda e: 4*e/(np.pi * (3*(1+e) - np.sqrt((3*e+1)*(e+3))))
+xs = np.linspace(0, 1, 100)
+
+plt.figure(figsize = (10, 8), dpi = 300)
+plt.rc('font', size = 20)
+plt.scatter(normal['elongation'], normal['score'], marker = '.')
+plt.scatter(thin['elongation'], thin['score'], marker = 'x')
+plt.scatter(mnist['elongation'], mnist['score'], marker = '^')
+plt.scatter(mostlyconvex['elongation'], mostlyconvex['score'], marker = '+')
+plt.plot(xs, f(xs), 'b--')
+plt.legend(['Normal', 'Thin', 'MNIST', 'Mostlyconvex', 'Ellipses'])
+plt.xlabel('Elongation')
+plt.ylabel('Awesomeness')
+plt.savefig('ae.png', bbox_inches = 'tight')

### 2024-10-18 scripts/plot-cae.py

@@ -1,0 +1,31 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+import pandas as pd
+import sqlite3
+
+with sqlite3.connect('glyphs.db') as db:
+    general = pd.read_sql_query('select * from pores where lfer > 0.9', db)
+
+shit = pd.read_csv('score.csv')
+data = general.merge(shit, on = 'label', how = 'inner', validate = "1:1")
+
+normal = data.query('name == "normal/"')
+thin = data.query('name == "thin/"')
+mnist = data.query('name == "mnist/"')
+mostlyconvex = data.query('name == "mostlyconvex/"')
+
+fig = plt.figure(figsize = (10, 9), dpi = 300)
+plt.rc('font', size = 14)
+ax = fig.add_subplot(projection = '3d')
+ax.scatter(normal['convexity'], normal['elongation'], normal['score'], marker = '.')
+ax.scatter(thin['convexity'], thin['elongation'], thin['score'], marker = 'x')
+ax.scatter(mnist['convexity'], mnist['elongation'], mnist['score'], marker = '^')
+ax.scatter(mostlyconvex['convexity'], mostlyconvex['elongation'], mostlyconvex['score'], marker = '+')
+ax.set_xlabel('Convexity')
+ax.set_ylabel('Elongation')
+ax.set_zlabel('Awesomeness')
+ax.view_init(elev = 18, azim = -40, roll = 0)
+ax.legend(['Normal', 'Thin', 'MNIST', 'Mostlyconvex'], markerscale = 2.5)
+plt.savefig('cae.png', bbox_inches = 'tight', pad_inches = 0.4)

### 2024-10-18 paper.tex
Further progress

@@
   p = \inf \{p_{AB} \ \forall (A, B) \in B^2\}
+  \label{eq:awesomeness}
 \end{equation}
@@
 \section{Results}
-We computed \highlight{awesomness} for 4000 synthetically generated images with
+We computed \highlight{awesomeness} for 4000 synthetically generated images with
 dimensions $1000 \times 1000$ pixels (1000 images from 4 different
@@
 
-\section{Comparison with other parameters}
-\highlight{CEA vs CER}.
+Summarly 3901 images out of 4000 (97.5\%) were good enough for \texttt{sort} to
+sort boundary points in pores. For these images we also computed commonly used
+convexity and elongation parameters. On \cref{fig:cae-space} each pore is
+represented as a dot in convexity-elongation-\highlight{awesomeness} (CEA)
+space.
+\begin{figure*}
+  \centering
+  \subfigure[Convexity-elongation-\highlight{awesomeness} space]{
+    \includegraphics[width=0.4\linewidth]{images/cae.png}
+    \label{fig:cae-space}}
+  \hfill
+  \subfigure[Convexity-elongation-roundness space]{
+    \includegraphics[width=0.4\linewidth]{images/cer.png}
+    \label{fig:cer-space}}
+  \vskip\baselineskip
+  \subfigure[Elongation-\highlight{Awesomeness} space]{
+    \includegraphics[width=0.4\linewidth]{images/ae.png}
+    \label{fig:ae-space}}
+  \hfill
+  \subfigure[Convexity-elongation-\highlight{improved awesomeness} space]{
+    \includegraphics[width=0.4\linewidth]{images/caei.png}
+    \label{fig:caei-space}}
+  \caption[]{Synthetically generated pores shown as points in different
+    parameter spaces.}
+  \label{fig:parameter-spaces}
+\end{figure*}
+
+It can be seen that if a pore has low convexity ($< 0.6$)
+\highlight{awesomeness} adds no information to the pore's descriptors because it
+stays relatively low for all pores. When, however, the convexity is high it adds
+a new dimension to the parameter space. \highlight{Awesomeness} also correlates
+with elongation, but this correlation can be reduced. Remember, that a disk has
+the biggest known \highlight{awesomeness}. Similarly, an ellipse defined as
+\begin{equation*}
+  \frac{x^2}{a^2} + \frac{y^2}{b^2} = 1
+\end{equation*}
+has the biggest known \highlight{awesomeness} from all shapes with elongation
+$E = a / b$ (suppose $a \le b$) (see \cref{fig:ae-space}). Using Ramanujan's
+formular for the perimeter of an ellipse we get
+\begin{equation*}
+  p \le p_{ellipse} = \frac{2a}{P/2} \approx \frac{4E}{\pi[3(1+E) - \sqrt{(3E+1)(E+3)}]}
+\end{equation*}
+By dividing \highlight{awesomeness} by $p_{ellipse}$ we obtain an improved
+parameter $p'$:
+\begin{equation}
+  p' = \frac{\pi p [3(1+E) - \sqrt{(3E+1)(E+3)}]}{4E}
+  \label{eq:improved-awesomeness}
+\end{equation}
+Indeed, on \cref{fig:caei-space} we see that improved awesomeness is less
+correlated with elongation.
+
+Another common parameter for describing pore shapes is roundness. Figure
+\ref{fig:cer-space} features convexity-elongation-roundness (CER) space.
+It can be seen that roundness-convexity correlation is bigger than
+awesomeness-convexity correlation. All correlation values are in
+\cref{tab:correlations}.
+\begin{table*}[!htp]
+  \centering
+  \begin{tabular}{|c|c|c|c|c|}
+    \hline
+    & Awesomeness & Elongation & Convexity & Roundness \\
+    \hline
+    Awesomeness & 1 & 0.049 & 0.557 & 0.745 \\
+    \hline
+    Elongation & & 1 & 0.457 & 0.355 \\
+    \hline
+    Convexity &&& 1 & 0.922 \\
+    \hline
+    Roundness &&&& 1 \\
+    \hline
+  \end{tabular}
+  \caption{Correlation between shape describing parameters.}
+  \label{tab:correlations}
+\end{table*}
+
+To test abilities of the awesomeness parameter we now divide our pores in groups
+with different convexity. The first group has pores with convexity $0.55 \le C < 0.65$,
+the second -- $0.65 \le C < 0.75$, the third -- $0.75 \le C < 0.85$ and the fourth
+-- $0.85 \le C < 0.95$. Five images with the biggest awesomeness and five images
+with the smallest awesomeness from each group are shown on \highlight{image
+  number 100500}.
 

### 2024-10-18 scripts/plot-ae.py

@@ -20,13 +20,13 @@ f = lambda e: 4*e/(np.pi * (3*(1+e) - np.sqrt((3*e+1)*(e+3))))
 xs = np.linspace(0, 1, 100)
 
 plt.figure(figsize = (10, 8), dpi = 300)
-plt.rc('font', size = 20)
+plt.rc('font', size = 17)
 plt.scatter(normal['elongation'], normal['score'], marker = '.')
 plt.scatter(thin['elongation'], thin['score'], marker = 'x')
 plt.scatter(mnist['elongation'], mnist['score'], marker = '^')
 plt.scatter(mostlyconvex['elongation'], mostlyconvex['score'], marker = '+')
 plt.plot(xs, f(xs), 'b--')
-plt.legend(['Normal', 'Thin', 'MNIST', 'Mostlyconvex', 'Ellipses'])
+plt.legend(['Normal', 'Thin', 'MNIST', 'Mostlyconvex', 'Ellipses'], markerscale = 2.5)
 plt.xlabel('Elongation')
 plt.ylabel('Awesomeness')
 plt.savefig('ae.png', bbox_inches = 'tight')

### 2024-10-18 scripts/plot-cae.py

@@ -5,11 +5,15 @@ import matplotlib.pyplot as plt
 import pandas as pd
 import sqlite3
 
+f = lambda e: 4*e/(np.pi * (3*(1+e) - np.sqrt((3*e+1) * (e+3))))
+
 with sqlite3.connect('glyphs.db') as db:
     general = pd.read_sql_query('select * from pores where lfer > 0.9', db)
 
 shit = pd.read_csv('score.csv')
 data = general.merge(shit, on = 'label', how = 'inner', validate = "1:1")
+
+data['score'] = data['score'] / f(data['elongation'])
 
 normal = data.query('name == "normal/"')
 thin = data.query('name == "thin/"')
@@ -17,15 +21,15 @@ mnist = data.query('name == "mnist/"')
 mostlyconvex = data.query('name == "mostlyconvex/"')
 
 fig = plt.figure(figsize = (10, 9), dpi = 300)
-plt.rc('font', size = 14)
+plt.rc('font', size = 17)
 ax = fig.add_subplot(projection = '3d')
+ax.view_init(elev = 18, azim = -40, roll = 0)
 ax.scatter(normal['convexity'], normal['elongation'], normal['score'], marker = '.')
 ax.scatter(thin['convexity'], thin['elongation'], thin['score'], marker = 'x')
 ax.scatter(mnist['convexity'], mnist['elongation'], mnist['score'], marker = '^')
 ax.scatter(mostlyconvex['convexity'], mostlyconvex['elongation'], mostlyconvex['score'], marker = '+')
-ax.set_xlabel('Convexity')
-ax.set_ylabel('Elongation')
+ax.set_xlabel('\nConvexity', linespacing = 2)
+ax.set_ylabel('\nElongation', linespacing = 2)
 ax.set_zlabel('Awesomeness')
-ax.view_init(elev = 18, azim = -40, roll = 0)
 ax.legend(['Normal', 'Thin', 'MNIST', 'Mostlyconvex'], markerscale = 2.5)
-plt.savefig('cae.png', bbox_inches = 'tight', pad_inches = 0.4)
+plt.savefig('caei.png', bbox_inches = 'tight', pad_inches = 0.4)

### 2024-10-18 scripts/plot-cer.py

@@ -1,0 +1,28 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+import pandas as pd
+import sqlite3
+
+with sqlite3.connect('glyphs.db') as db:
+    data = pd.read_sql_query('select * from pores where lfer > 0.9', db)
+
+normal = data.query('name == "normal/"')
+thin = data.query('name == "thin/"')
+mnist = data.query('name == "mnist/"')
+mostlyconvex = data.query('name == "mostlyconvex/"')
+
+fig = plt.figure(figsize = (10, 9), dpi = 300)
+plt.rc('font', size = 17)
+ax = fig.add_subplot(projection = '3d')
+ax.view_init(elev = 18, azim = -40, roll = 0)
+ax.scatter(normal['convexity'], normal['elongation'], normal['sphericity'], marker = '.')
+ax.scatter(thin['convexity'], thin['elongation'], thin['sphericity'], marker = 'x')
+ax.scatter(mnist['convexity'], mnist['elongation'], mnist['sphericity'], marker = '^')
+ax.scatter(mostlyconvex['convexity'], mostlyconvex['elongation'], mostlyconvex['sphericity'], marker = '+')
+ax.set_xlabel('\nConvexity', linespacing = 2)
+ax.set_ylabel('\nElongation', linespacing = 2)
+ax.set_zlabel('Roundness')
+ax.legend(['Normal', 'Thin', 'MNIST', 'Mostlyconvex'], markerscale = 2.5)
+plt.savefig('cer.png', bbox_inches = 'tight', pad_inches = 0.4)

### 2024-10-21 paper.tex
Invert images of pores
Further progress

@@
   \subfigure[\texttt{normal}]{
-    \includegraphics[width=0.4\linewidth]{images/normal.png}}
+    \includegraphics[width=0.4\linewidth,frame]{images/normal.png}}
   \subfigure[\texttt{thin}]{
-    \includegraphics[width=0.4\linewidth]{images/thin.png}}
+    \includegraphics[width=0.4\linewidth,frame]{images/thin.png}}
   \vskip\baselineskip
   \subfigure[\texttt{mnist}]{
-    \includegraphics[width=0.4\linewidth]{images/mnist.png}}
+    \includegraphics[width=0.4\linewidth,frame]{images/mnist.png}}
   \subfigure[\texttt{mostlyconvex}]{
-    \includegraphics[width=0.4\linewidth]{images/mostlyconvex.png}}
+    \includegraphics[width=0.4\linewidth,frame]{images/mostlyconvex.png}}
   \caption[]{One pore from each dataset used for calculation of
@@
 -- $0.85 \le C < 0.95$. Five images with the biggest awesomeness and five images
-with the smallest awesomeness from each group are shown on \highlight{image
-  number 100500}.
+with the smallest awesomeness from each group are shown on
+\cref{fig:convexity-groups-score}. It can be clearly seen that pores with higher
+values of \highlight{awesomeness} are more ``solid'' and more finely
+clusterized.
+
+For comparison, we do the same sorting across groups for roundness
+parameter. The results are on
+\cref{fig:convexity-groups-roundness}. Well-clusterized pores have the biggest
+roundness for convexity $C > 0.8$. For lower convexity, however, even pores with
+the biggest roundness in the group are also underclusterized while
+\highlight{awesomeness} parameter is capable of separating well-clusterized and
+underclusterized pores.
+\begin{figure*}
+  \centering
+  \subfigure[$0.55 \le C < 0.65$]{
+    \includegraphics[width=0.4\linewidth]{images/groups-score-0.60.png}}
+  \hfill
+  \subfigure[$0.65 \le C < 0.75$]{
+    \includegraphics[width=0.4\linewidth]{images/groups-score-0.70.png}}
+  \vskip\baselineskip
+  \subfigure[$0.75 \le C < 0.85$]{
+    \includegraphics[width=0.4\linewidth]{images/groups-score-0.80.png}}
+  \hfill
+  \subfigure[$0.85 \le C < 0.95$]{
+    \includegraphics[width=0.4\linewidth]{images/groups-score-0.90.png}}
+  \caption[]{Pores divided into groups by their convexity. Upper row of each
+    subfigure: pores with minimal \highlight{awesomeness} in the group, lower
+    row: pores with maximal \highlight{awesomeness} in the group.}
+  \label{fig:convexity-groups-score}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \subfigure[$0.55 \le C < 0.65$]{
+    \includegraphics[width=0.4\linewidth]{images/groups-sphericity-0.60.png}}
+  \hfill
+  \subfigure[$0.65 \le C < 0.75$]{
+    \includegraphics[width=0.4\linewidth]{images/groups-sphericity-0.70.png}}
+  \vskip\baselineskip
+  \subfigure[$0.75 \le C < 0.85$]{
+    \includegraphics[width=0.4\linewidth]{images/groups-sphericity-0.80.png}}
+  \hfill
+  \subfigure[$0.85 \le C < 0.95$]{
+    \includegraphics[width=0.4\linewidth]{images/groups-sphericity-0.90.png}}
+  \caption[]{Pores divided into groups by their convexity. Upper row of each
+    subfigure: pores with minimal roundness in the group, lower row: pores with
+    maximal roundness in the group.}
+  \label{fig:convexity-groups-roundness}
+\end{figure*}
 

### 2024-10-21 paper.tex
Summary

@@
   \subfigure[$0.55 \le C < 0.65$]{
-    \includegraphics[width=0.4\linewidth]{images/groups-score-0.60.png}}
+    \includegraphics[width=0.4\linewidth]{images/groups-score-0.60.png}
+    \label{fig:small-gap}}
   \hfill
@@
   \subfigure[$0.85 \le C < 0.95$]{
-    \includegraphics[width=0.4\linewidth]{images/groups-score-0.90.png}}
+    \includegraphics[width=0.4\linewidth]{images/groups-score-0.90.png}
+    \label{fig:small-blob}}
   \caption[]{Pores divided into groups by their convexity. Upper row of each
@@
 
+\section{Summary}
+In this paper we have developed a new parameter for assession of pore
+clusterization quality which can be used as a replacement for roundness
+parameter. Benefits of this parameter include:
+\begin{itemize}
+\item Lower absoulute value of correlation with other common parameters, such as
+  convexity, elongation and roundness.
+\item Ease of computation.
+\item Ability to precisely separate well-clusterized pores and underclusterized
+  pores in a high convexity range, even if roundness fails to do so.
+\item Rotation and resize invariance.
+\end{itemize}
+
+Flaws of this parameter include:
+\begin{itemize}
+\item C-shaped pores with a small gap, like the pore on the left-top of
+  \cref{fig:small-gap} always have small \highlight{awesomeness}, even if they
+  are otherwise clusterized correctly.
+\item Small changes to an image of a pore, when cleverly done, can make drastic
+  changes in \highlight{awesomeness}.
+\end{itemize}
+
+The first flaw can be dealt with by replacing the Euclidean distance in
+\cref{eq:intro} with the length of the shortest path between points which does
+not cross the pore's boundary. This, however, can increase computational time
+significantly.
+
+The second flaw means that a pore with a very small attachment (compared to the
+pore's total surface) connected with a thin throat to the pore's main body has
+low \highlight{awesomeness}, like the third pore on \cref{fig:small-blob}, a row
+on the top. Normally, small attachments like this do not contribute to any
+physical process in any way, so they can simply be ignored and, therefore, their
+impact on \highlight{awesomeness} may be not justified.
+
 \bibliography{paper}

### 2024-10-22 paper.tex
Expand introduction

@@
   to the Skvortsova's parameter}.
+
+In this paper we also use the following common parameters which are used to
+describe pore shapes:
+\begin{itemize}
+\item Convexity $C$ is a relation between surface of a pore and surface bounded
+  by its convex hull.
+\item Roundness $R$ is a relation between perimeter of a disk which has the same
+  surface as a pore to perimeter of that pore.
+\item Elongation $E$ is a relation between eigenvalues of a matrix $A$ with the
+  smallest and the biggest absolute values. $A$ is a $2 \times 2$ covariation
+  matrix of coordinates of pore points. For a discrete image of a pore its
+  elements equal to
+  \begin{equation*}
+    a_{ij} = \sum_{x \in \left\{
+      \begin{array}{l}
+        \text{Coordinates of points} \\
+        \text{belonging to the pore}
+      \end{array}
+      \right\}} (x_i - \overline{x_i})(x_j - \overline{x_j})
+  \end{equation*}
+\end{itemize}
+All of these parameters lie in the range $[0, 1]$.
 

### 2024-10-22 paper.tex
Bottle neck -> bottleneck

@@
 We propose a new parameter for shape description which is based on the idea of
-numerical assession of bottle necks in pores. For simplicity, we will assume
+numerical assession of bottlenecks in pores. For simplicity, we will assume
 that our pore is 1-connected. Suppose you have a round pore in the form close to
@@
 second. For this purpose we want to visit all points which lie on the pore's
-boundary and find a pair of points which form a bottle neck and have a small
+boundary and find a pair of points which form a bottleneck and have a small
 distance between each other. Obviously, not all pairs of points which are close
-to each other form a bottle neck. Namely, on \cref{fig:parameter} points $A$ and
-$B$ form a bottle neck and points $A$ and $C$ do not form it. If you choose a
+to each other form a bottleneck. Namely, on \cref{fig:parameter} points $A$ and
+$B$ form a bottleneck and points $A$ and $C$ do not form it. If you choose a
 point $O$ which lies outside of the pore and travel along the pore's boundary in
@@
 to your right (or vice-versa). But if you are at $A$ or $C$ you will see $O$ to
-the same side from you. Instead of doing this check for ``bottle-neckness'', we
+the same side from you. Instead of doing this check for ``bottleneckness'', we
 add a penalty coefficient to the distance between points, namely for a pair of
@@
   \caption[]{A dumbbell-like boundary of a pore. Points $A$ and $B$ form a
-    bottle neck while points $A$ and $C$ do not. This can seen by a relative
+    bottleneck while points $A$ and $C$ do not. This can seen by a relative
     position of the point $O$ while traversing the boundary

### 2024-10-22 paper.tex
Small improvements

@@
 second. For this purpose we want to visit all points which lie on the pore's
-boundary and find a pair of points which form a bottleneck and have a small
+boundary and find a pair of points which form a bottleneck, i.e have a small
 distance between each other. Obviously, not all pairs of points which are close
@@
     \State \textbf{return} \texttt{pmin(\%bs)}
+    \Comment The final step is in \cref{alg:pmin}.
     \EndProcedure
@@
 \begin{equation*}
+  \left\{
   \begin{aligned}
@@
   \end{aligned}
+  \right.
 \end{equation*}
@@
 and $B_2 = \begin{pmatrix} f \\ g \end{pmatrix}(t_2)$. The sorting in the step 2
-implies that if $t_1 < t_2$, the point $B_1$ must appear before $B_2$ in $bs$.
+implies that if $t_1 < t_2$, the point $B_1$ must appear before $B_2$ in
+\texttt{\%bs}.
 
 In the following algorithms we will use a notion of single linked lists (or
-simply lists). A list of elements of type $a$ can be defined using the following
-data type with two constructors, \texttt{[]} and \texttt{(:)}:
+simply lists). A list of elements of type \texttt{a} can be defined using the
+following data type with two constructors, \texttt{[]} and \texttt{(:)}:
 \begin{verbatim}
@@
 The first constructor creates an empty list and the second attaches an element
-of type $a$ to the list of elements of type $a$. Sometimes we will use
-conventional functions for working with lists such as \texttt{head},
+of type \texttt{a} to the list of elements of type \texttt{a}. Sometimes we will
+use conventional functions for working with lists such as \texttt{head},
 \texttt{tail}, \texttt{map}, \texttt{foldl} and so on.
@@
 points have Chebyshev distance equal to 1. This is done by making a list which
-contains some (maybe random) point on the boundary and successive addition
-neighbor points (relative to the head of that list) to the list. It may be that
-all neighbors must be tried to successfully construct the sorted list.
+contains some (maybe random) point belonging to the boundary and successive
+addition of neighbor points (relative to the head of that list) to the list. It
+may be that all neighbors must be tried to successfully construct the sorted
+list.
 
@@
 example, an image is taken with bad resolution (i.e. pores consist only of a few
-pixels) some quality improving techniques must be applied first.
+pixels) some quality improving techniques must be applied first. It also
+exploits the commutative property $p_{AB} = p_{BA}$.
 \begin{algorithm}[H]

### 2024-10-22 paper.tex
Rework definition of awesomeness (1/N)

@@
 $B$ is a set of all points on the pore's boundary. We define a new pore shape
-parameter $p$, called ``\highlight{awesomeness}'', using \ref{eq:intro}:
+parameter $p$ using \ref{eq:intro}:
 \begin{equation}
   p = \inf \{p_{AB} \ \forall (A, B) \in B^2\}
-  \label{eq:awesomeness}
+  \label{eq:pre-awesomeness}
 \end{equation}
@@
 \end{figure}
+
+Although a guaranteed upper bound for $p$ is 1, it's reachable only for
+degenerate shapes in the form of line segments. The biggest value for
+non-degenerate shapes is reached for a disk and equals to $2/\pi$. Similarly, an
+ellipse defined as
+\begin{equation*}
+  \frac{x^2}{a^2} + \frac{y^2}{b^2} = 1
+\end{equation*}
+has the biggest known value of $p$ from all shapes with elongation $E = a / b$
+(suppose $a \le b$). Using Ramanujan's formula for the perimeter of an ellipse
+we get
+\begin{equation*}
+  p \le p_{ellipse} = \frac{2a}{P/2} \approx \frac{4E}{\pi[3(1+E) - \sqrt{(3E+1)(E+3)}]}
+\end{equation*}
+where $P$ is a perimeter of the ellipse. By dividing $p$ by $p_{ellipse}$ we
+obtain an improved pore shape parameter $P$:
+\begin{equation*}
+  P = \frac{\pi p [3(1+E) - \sqrt{(3E+1)(E+3)}]}{4E}
+\end{equation*}
+
+Substituting \cref{eq:pre-awesomeness} and \cref{eq:intro} we get a new pore
+shape parameter we call ``\highlight{awesomeness}'':
+\begin{equation}
+  \begin{aligned}
+    P &= \frac{\pi [3(1+E) - \sqrt{(3E+1)(E+3)}]}{4E} \times \\
+    & \times \inf \{\frac{\rho_{AB}}{L_{AB}} \ \forall (A, B) \in B^2\}
+  \end{aligned}
+  \label{eq:awesomeness}
+\end{equation}
+where, again, $E$ is the elongation and $B$ is the boundary of the pore.
 
@@
 
-Although a guaranteed upper bound for awesomeness is 1, it's reachable only for
-degenerate shapes in the form of line segments. The biggest value for
-non-degenerate shapes is reached for a disk and equals to $2/\pi$.
-
 \section{Results}
@@
 stays relatively low for all pores. When, however, the convexity is high it adds
-a new dimension to the parameter space. \highlight{Awesomeness} also correlates
-with elongation, but this correlation can be reduced. Remember, that a disk has
-the biggest known \highlight{awesomeness}. Similarly, an ellipse defined as
-\begin{equation*}
-  \frac{x^2}{a^2} + \frac{y^2}{b^2} = 1
-\end{equation*}
-has the biggest known \highlight{awesomeness} from all shapes with elongation
-$E = a / b$ (suppose $a \le b$) (see \cref{fig:ae-space}). Using Ramanujan's
-formular for the perimeter of an ellipse we get
-\begin{equation*}
-  p \le p_{ellipse} = \frac{2a}{P/2} \approx \frac{4E}{\pi[3(1+E) - \sqrt{(3E+1)(E+3)}]}
-\end{equation*}
-By dividing \highlight{awesomeness} by $p_{ellipse}$ we obtain an improved
-parameter $p'$:
-\begin{equation}
-  p' = \frac{\pi p [3(1+E) - \sqrt{(3E+1)(E+3)}]}{4E}
-  \label{eq:improved-awesomeness}
-\end{equation}
+a new dimension to the parameter space.
+
+% CHECK THIS:
 Indeed, on \cref{fig:caei-space} we see that improved awesomeness is less

### 2024-10-22 paper.tex
Rework definition of awesomeness (2/N)

@@
 \end{equation}
-where, again, $E$ is the elongation and $B$ is the boundary of the pore.
+where, again, $E$ and $B$ are the elongation the boundary of the pore,
+$\rho_{AB}$ is the Euclidean distance between points $A$ and $B$ and $L_{AB}$ is
+the length of a path (the shortest one) between $A$ and $B$ along the boundary.
 
@@
     \Comment Sort points as described in \cref{alg:sort}.
-    \State \textbf{return} \texttt{pmin(\%bs)}
-    \Comment The final step is in \cref{alg:pmin}.
+    \State \textbf{return} \texttt{c $\cdot$ pmin(\%bs)}
+    \Comment The final step is in \cref{alg:pmin}. \texttt{c} is the fraction in
+    \cref{eq:awesomeness}.
     \EndProcedure
@@
   \vskip\baselineskip
-  \subfigure[Elongation-\highlight{Awesomeness} space]{
+  \subfigure[Elongation-\highlight{Correlated awesomeness} space]{
     \includegraphics[width=0.4\linewidth]{images/ae.png}
     \label{fig:ae-space}}
-  \hfill
-  \subfigure[Convexity-elongation-\highlight{improved awesomeness} space]{
-    \includegraphics[width=0.4\linewidth]{images/caei.png}
-    \label{fig:caei-space}}
   \caption[]{Synthetically generated pores shown as points in different
@@
 
-% CHECK THIS:
-Indeed, on \cref{fig:caei-space} we see that improved awesomeness is less
-correlated with elongation.
-
 Another common parameter for describing pore shapes is roundness. Figure
@@
 \cref{tab:correlations}.
+
+On \cref{fig:ae-space} pores are shown in $p-E$ space where $p$ is a
+``correlated'' \highlight{awesomeness} parameter \cref{eq:pre-awesomeness}. It
+shows that our assumption on the maximal value of \highlight{awesomeness} is
+correct indeed.
+
 \begin{table*}[!htp]

### 2024-11-08 paper.tex
Small improvement
Fix elongation definition

@@
   surface as a pore to perimeter of that pore.
-\item Elongation $E$ is a relation between eigenvalues of a matrix $A$ with the
-  smallest and the biggest absolute values. $A$ is a $2 \times 2$ covariation
-  matrix of coordinates of pore points. For a discrete image of a pore its
-  elements equal to
+\item Elongation $E$ is a square root of a relation
+  $|\frac{\lambda_1}{\lambda_2}|$ where $\lambda_1$ and $\lambda_2$ are two
+  eigenvalues of a matrix $A$ which is a $2 \times 2$ covariation matrix of
+  coordinates of pore points. For a discrete image of a pore its elements equal
+  to
   \begin{equation*}
@@
   \end{equation*}
+  Eigenvalues are enumerated so that $E$ is no bigger than $1$.
 \end{itemize}
@@
   convexity, elongation and roundness.
-\item Ease of computation.
+\item Ease of computation and interpretation.
 \item Ability to precisely separate well-clusterized pores and underclusterized

### 2024-11-08 paper.tex
Remove two words
Improve the parameter

@@
 to each other form a bottleneck. Namely, on \cref{fig:parameter} points $A$ and
-$B$ form a bottleneck and points $A$ and $C$ do not form it. If you choose a
-point $O$ which lies outside of the pore and travel along the pore's boundary in
-one direction (either clockwise or counter-clockwise), when you arrive at $A$
-you will see the point $O$ to your left and when you are in $B$ you will see $O$
-to your right (or vice-versa). But if you are at $A$ or $C$ you will see $O$ to
-the same side from you. Instead of doing this check for ``bottleneckness'', we
-add a penalty coefficient to the distance between points, namely for a pair of
-points $(A, B)$ we calculate the following:
+$B$ form a bottleneck and points $A$ and $C$ do not. If you choose a point $O$
+which lies outside of the pore and travel along the pore's boundary in one
+direction (either clockwise or counter-clockwise), when you arrive at $A$ you
+will see the point $O$ to your left and when you are in $B$ you will see $O$ to
+your right (or vice-versa). But if you are at $A$ or $C$ you will see $O$ to the
+same side from you. Instead of doing this check for ``bottleneckness'', we add a
+penalty coefficient to the distance between points, namely for a pair of points
+$(A, B)$ we calculate the following:
 \begin{equation}
@@
 \begin{equation}
-  p = \inf \{p_{AB} \ \forall (A, B) \in B^2\}
+  p = \inf \{ p_{AB} \ \forall (A, B) \in B^2 : 2 L_{AB} \ge cP \}
   \label{eq:pre-awesomeness}
 \end{equation}
+The condition on a pair of points $(A, B)$ is that the ``boundary distance''
+between them must be no less than $\frac{cP}{2}$ where $P$ is a perimeter of a
+pore and $c \in [0,1]$ is some parameter. This parameter is introduced to
+prevent small features of the boundary from affecting $p$. In this paper we will
+use $c = 0.1$. A value $c = 0$ means there are no restrictions on $(A, B)$.
+
 Obviously, it's unlikely that $p$ = $p_{AC}$ because $L_{AC} \approx \rho_{AC}$.
@@
     P &= \frac{\pi [3(1+E) - \sqrt{(3E+1)(E+3)}]}{4E} \times \\
-    & \times \inf \{\frac{\rho_{AB}}{L_{AB}} \ \forall (A, B) \in B^2\}
+    & \times \inf \{\frac{\rho_{AB}}{L_{AB}} \ \forall (A, B) \in B^2 : 2
+    L_{AB} \ge cP \}
   \end{aligned}
@@
 \end{equation}
-where, again, $E$ and $B$ are the elongation the boundary of the pore,
+where, again, $E$ and $B$ are the elongation and the boundary of the pore,
 $\rho_{AB}$ is the Euclidean distance between points $A$ and $B$ and $L_{AB}$ is
@@
   are otherwise clusterized correctly.
-\item Small changes to an image of a pore, when cleverly done, can make drastic
-  changes in \highlight{awesomeness}.
 \end{itemize}
@@
 
-The second flaw means that a pore with a very small attachment (compared to the
-pore's total surface) connected with a thin throat to the pore's main body has
-low \highlight{awesomeness}, like the third pore on \cref{fig:small-blob}, a row
-on the top. Normally, small attachments like this do not contribute to any
-physical process in any way, so they can simply be ignored and, therefore, their
-impact on \highlight{awesomeness} may be not justified.
-
 \bibliography{paper}

### 2024-11-08 paper.tex
Update algorithm description

@@
     \Comment Sort points as described in \cref{alg:sort}.
-    \State \textbf{return} \texttt{c $\cdot$ pmin(\%bs)}
-    \Comment The final step is in \cref{alg:pmin}. \texttt{c} is the fraction in
+    \State \textbf{return} \texttt{m $\cdot$ pmin(\%bs)}
+    \Comment The final step is in \cref{alg:pmin}. \texttt{m} is the fraction in
     \cref{eq:awesomeness}.
@@
 step minimizes $p_{AB}$ parameter for each pair of points $(A, B)$ which lie on
-the boundary.
+the boundary (wtih respect to constraints introduced by the parameter $c$).
 
@@
     \If{\texttt{tree\_empty\_p(tree)}}
-    \State \textbf{return} \texttt{sorted}
+    \State \textbf{return} \texttt{Just sorted}
     \Comment No more unsorted points, we are finished.
@@
     \If{\texttt{notevery(check\_dist, neighbors)}}
-    \State \textbf{return} \texttt{[]}
+    \State \textbf{return} \texttt{Nothing}
     \Comment We have failed, try to sort another way
@@
     \State \texttt{sorted $\gets$ map(\%go, ns)}
-    \State \textbf{return} The first non-empty list from \texttt{sorted}, if
-    any. Otherwise return \texttt{[]}.
+    \State \textbf{return} The first \texttt{Just} value from \texttt{sorted},
+    if any. Otherwise return \texttt{Nothing}.
     \EndProcedure
@@
 list do not represent a simple closed curve (like on \cref{fig:good-and-bad}),
-\texttt{sort} will return an empty list.
+\texttt{sort} will return \texttt{Nothing}, otherwise a sorted list is returned
+wrapped in \texttt{Just}.
 \begin{figure}[tp]
@@
     \EndProcedure
-    \Procedure{\texttt{perimeter}}{\texttt{points}}
-    \State \texttt{p1 $\gets$ foldl((+), 0, pairwise\_distances(points))}
+    \Procedure{\texttt{perimeter}}{\texttt{points, c}}
+    \State \texttt{p1 $\gets$ foldl1((+), pairwise\_distances(points))}
     \State \texttt{p2 $\gets$ dist(head(points), last(points))}
@@
     \EndProcedure
-    \Procedure{\texttt{minimize\_on\_head}}{\texttt{acc, p, points}}
+    \Procedure{\texttt{minimize\_on\_head}}{\texttt{acc, p, bds, points}}
     \Comment \texttt{acc} is the best (minimal) parameter found so far,
-    \texttt{p} is a perimeter of the boundary.
+    \texttt{p} is a perimeter of the boundary, \texttt{bds} is a list of
+    distances along the boundary from the head of \texttt{points} to all points
+    in \texttt{tail(points)}.
     \Procedure{\texttt{go}}{\texttt{acc, x}}
-    \State \texttt{(point, boundary\_dist) $\gets$ x}
-    \State \texttt{awesomeness $\gets$ dist(point, head(points)) /
-      min(boundary\_dist, p - boundary\_dist)}
-    \State \textbf{return} \texttt{min(acc, awesomeness)}
+    \State \texttt{(point, bd) $\gets$ x}
+    \State \texttt{\%bd $\gets$ min(bd, p - bd)}
+    \If{\texttt{\%bd < c/2 $\cdot$ p}}
+    \State \textbf{return} \texttt{acc}
+    \Else
+    \State \texttt{param $\gets$ dist(point, head(points)) / \%bd}
+    \State \textbf{return} \texttt{min(acc, param)}
+    \EndIf
     \EndProcedure
-    \State \texttt{ds $\gets$ scanl((+), 0, pairwise\_distances(points))}
-    \State \texttt{tmp $\gets$ zip(tail(points), tail(ds))}
+    \State \texttt{tmp $\gets$ zip(tail(points), ds)}
     \State \textbf{return} \texttt{foldl(go, acc, tmp)}
@@
     \State \texttt{p $\gets$ perimeter(points)}
+    \State \texttt{bds $\gets$ scanl1((+), pairwise\_distances(points))}
     \Procedure{\texttt{go}}{\texttt{acc, points}}
-    \State \textbf{return} \texttt{minimize\_on\_head(acc, p, points)}
+    \State \texttt{(param, bds) $\gets$ acc}
+    \State \texttt{\%param $\gets$ minimize\_on\_head(param, p, bds, points)}
+    \State \texttt{\%bds  $\gets$ map(subtract(head(bds)), tail(bds))}
+    \State \textbf{return} \texttt{(\%param, \%bds)}
     \EndProcedure
-    \State \textbf{return} \texttt{foldl(go, +infinity, points)}
+    \State \textbf{return} \texttt{foldl(go, (+Inf, bds), tails(points))}
+    \Comment For a list \texttt{a = [1,2,3]} \texttt{tails(a)} returns
+    \texttt{[[1,2,3], [2,3], [3]]}.
     \EndProcedure
@@
 \end{algorithm}
-If \texttt{sort} cannot sort boundary points, \texttt{pmin} will return
-\texttt{+infinity}.
+
+Algorithmic complexity of \ref{alg:extraction} and \ref{alg:sort} is $O(n)$ and
+of \ref{alg:pmin} is $O(n^2)$.
 

### 2024-11-11 paper.tex
Table of ranges

@@
 
+Summarizing, we can divide pores into three groups by the quality of
+clusterization (see \cref{tab:ranges}).
+\begin{table*}[!htp]
+  \centering
+  \begin{tabular}{|c|c|}
+    \hline
+    \highlight{Awesomeness} & Comment \\
+    \hline
+    < 0.1 & Virtually many different pores connected by thin chords \\
+    \hline
+    0.1 - 0.6 & Pores which can be divides into subpores \\
+    \hline
+    > 0.6 & Well-clusterized pores \\
+    \hline
+  \end{tabular}
+  \caption{Different values of \highlight{awesomeness} and their meaning.}
+  \label{tab:ranges}
+\end{table*}
+
 \section{Summary}

### 2024-11-11 scripts/plot-min-max.py
Add a forgotten script

@@ -1,0 +1,54 @@
+#!/usr/bin/env python
+
+import matplotlib.pyplot as plt
+import matplotlib.ticker as ticker
+import numpy as np
+import pandas as pd
+import sqlite3
+from PIL import Image
+from PIL.ImageOps import invert
+import sys
+import os
+
+f = lambda e: 4*e/(np.pi * (3*(1+e) - np.sqrt((3*e+1) * (e+3))))
+
+what = sys.argv[1]
+how = sys.argv[2]
+mid = float(sys.argv[3])
+start = mid - 0.05
+end   = mid + 0.05
+
+with sqlite3.connect('glyphs.db') as db:
+    general = pd.read_sql_query('select * from pores where lfer > 0.9', db)
+
+shit = pd.read_csv('score.csv')
+data = general.merge(shit, on = 'label', how = 'inner', validate = "1:1")
+data['score'] = data['score'] / f(data['elongation'])
+
+query = 'convexity >= %f and convexity < %f' % (start, end)
+subdata = data.query(query).sort_values(what, axis = 0)
+
+print(subdata)
+
+plt.rc('font', size = 14)
+fig = plt.figure(figsize = (10, 4), dpi = 300)
+for i in range(5):
+    name = subdata.iloc[i]['label'] + '.pbm'
+    img = Image.open(os.path.expanduser(os.path.join('~', 'test', 'grains', name)))
+    ax = fig.add_subplot(2, 5, i+1)
+    ax.imshow(invert(img))
+    ax.title.set_text('$%s = %.4f$' % (how, subdata.iloc[i][what]))
+    ax.xaxis.set_major_locator(ticker.NullLocator())
+    ax.yaxis.set_major_locator(ticker.NullLocator())
+
+for i in range(5):
+    name = subdata.iloc[-i-1]['label'] + '.pbm'
+    img = Image.open(os.path.expanduser(os.path.join('~', 'test', 'grains', name)))
+    ax = fig.add_subplot(2, 5, i+6)
+    ax.imshow(invert(img))
+    ax.title.set_text('$%s = %.2f$' % (how, subdata.iloc[-i-1][what]))
+    ax.xaxis.set_major_locator(ticker.NullLocator())
+    ax.yaxis.set_major_locator(ticker.NullLocator())
+
+plt.subplots_adjust(wspace = 0.3, hspace = 0.05)
+plt.savefig('groups-%s-%.2f.png' % (what, mid), bbox_inches='tight')

### 2024-11-11 paper.tex
This is the end (no)

@@
 
+The parameter \cref{eq:awesomeness} is scale- and rotation-invariant. The
+algorithm presented in this paper changes the parameter by about 10\% when
+rotating an image of a pore or scaling it by a factor $0.5-2$. This inaccuracy
+is OK for assessing quality of pore clusterization, as can be seen in the next
+section.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.9\linewidth]{images/rotation-resize.png}
+  \caption[]{\highlight{Awesomeness} parameter for the same image under rotation
+  (red X marks) and resize (blue dot marks) transforms.}
+  \label{fig:rotation-resize}
+\end{figure}
+
 \section{Results}
@@
 \begin{itemize}
+\item Sometimes the shortest path between two points on a pore's boundary either:
+  \begin{itemize}
+  \item has more than two common points with the boundary;
+  \item lies entirely in the pore's exterior (with exception of end points).
+  \end{itemize}
+  In this case the two points definitely cannot form a bottleneck.
 \item C-shaped pores with a small gap, like the pore on the left-top of
@@
 
-The first flaw can be dealt with by replacing the Euclidean distance in
-\cref{eq:intro} with the length of the shortest path between points which does
-not cross the pore's boundary. This, however, can increase computational time
-significantly.
+The first flaw can be dealt with by replacing the Euclidean distance $\rho_{AB}$
+in \cref{eq:intro} with the length $d_{AB}$ of the shortest path between points
+which does not cross the pore's boundary. Although the resulting algorithm will
+have the same $O(n^2)$ complexity, doing so can increase computational time
+significantly. We call the parameter $P'$ with $d_{AB}$ in the place of
+$\rho_{AB}$ ``improved awesomeness''.
+
+We present an opensource solution for calculating \highlight{awesomeness} and
+improved \highlight{awesomeness}. \highlight{E-mail us and buy us coffee so we
+  can send this super program to you, no matter where you live! Hurry, this is a
+limited offer!} An average time for calculating \highlight{awesomeness} is 1
+second for a $1000 \times 1000$ png image and is $1-60$ seconds for calculating
+improved \highlight{awesomeness}.
 

### 2024-11-11 scripts/rotation-resize.py

@@ -1,0 +1,28 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+rot = np.load('rotate.npy')
+res = np.load('resize.npy')
+
+def err(a):
+    return (np.max(a) - np.min(a)) / np.mean(a)
+
+print(err(rot[:,1]))
+print(err(res[:,1]))
+
+res[:,0] = res[:,0] / 1000
+
+fig = plt.figure(figsize = (10, 8), dpi = 300)
+plt.rc('font', size = 17)
+#plt.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
+#plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
+ax1 = fig.gca()
+ax2 = ax1.twiny()
+ax1.scatter(rot[:,0], rot[:,1], c = 'r', marker = 'x')
+ax2.scatter(res[:,0], res[:,1], c = 'b')
+ax1.set_ylabel('Awesomeness')
+ax1.set_xlabel('Rotation angle, degrees')
+ax2.set_xlabel('Scale factor')
+plt.savefig('rotation-resize.png', bbox_inches = 'tight')

### 2024-11-11 paper.tex
More images

@@
 in \cref{eq:intro} with the length $d_{AB}$ of the shortest path between points
-which does not cross the pore's boundary. Although the resulting algorithm will
-have the same $O(n^2)$ complexity, doing so can increase computational time
-significantly. We call the parameter $P'$ with $d_{AB}$ in the place of
-$\rho_{AB}$ ``improved awesomeness''.
+which does not cross the pore's boundary (see \cref{fig:improved}). Although the
+resulting algorithm will have the same $O(n^2)$ complexity, doing so can
+increase computational time significantly. We call the parameter $P'$ with
+$d_{AB}$ in the place of $\rho_{AB}$ ``improved awesomeness''. The following
+relation always holds: $0 < P \le P' \le 1$.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.9\linewidth]{images/improved.png}
+  \caption[]{Pairs of points responsible for \highlight{awesomeness} (red) and
+    improved \highlight{awesomeness} (green).}
+  \label{fig:improved}
+\end{figure}
 

### 2024-11-11 paper.tex
Forgot a frame
Add a reference
Add a comment to pmin
Remove 'improved'

@@
 two such segments, you need to take the segment with minimal length). Suppose
-$B$ is a set of all points on the pore's boundary. We define a new pore shape
-parameter $p$ using \ref{eq:intro}:
+$B$ is a set of all points on the pore's boundary. We define a preliminary pore
+shape parameter $p$ using \ref{eq:intro}:
 \begin{equation}
@@
 where $P$ is a perimeter of the ellipse. By dividing $p$ by $p_{ellipse}$ we
-obtain an improved pore shape parameter $P$:
+obtain a parameter $P$:
 \begin{equation*}
@@
 implies that if $t_1 < t_2$, the point $B_1$ must appear before $B_2$ in
-\texttt{\%bs}.
+\texttt{\%bs} (denote it as $B_1 < B_2$).
 
@@
     \State \texttt{\%bds  $\gets$ map(subtract(head(bds)), tail(bds))}
+    \Comment $L_{B_2B_3} = L_{B_1B_3} - L_{B_1B_2}$ if $B_1 < B_2 < B_3$.
     \State \textbf{return} \texttt{(\%param, \%bds)}
@@
 algorithm presented in this paper changes the parameter by about 10\% when
-rotating an image of a pore or scaling it by a factor $0.5-2$. This inaccuracy
-is OK for assessing quality of pore clusterization, as can be seen in the next
-section.
+rotating an image of a pore or scaling it by a factor $0.5-2$ (see
+\cref{fig:rotation-resize}). This inaccuracy is OK for assessing quality of pore
+clusterization, as can be seen in the next section.
 \begin{figure}
@@
   \centering
-  \includegraphics[width=0.9\linewidth]{images/improved.png}
+  \includegraphics[width=0.9\linewidth,frame]{images/improved.png}
   \caption[]{Pairs of points responsible for \highlight{awesomeness} (red) and

### 2024-11-14 scripts/plot-ae.py
Awesomeness -> Narrowness + update plots (1/2)

@@ -28,5 +28,5 @@ plt.scatter(mostlyconvex['elongation'], mostlyconvex['score'], marker = '+')
 plt.plot(xs, f(xs), 'b--')
 plt.legend(['Normal', 'Thin', 'MNIST', 'Mostlyconvex', 'Ellipses'], markerscale = 2.5)
 plt.xlabel('Elongation')
-plt.ylabel('Awesomeness')
+plt.ylabel('Narrowness')
 plt.savefig('ae.png', bbox_inches = 'tight')

### 2024-11-14 scripts/plot-cae.py

@@ -5,15 +5,11 @@ import matplotlib.pyplot as plt
 import pandas as pd
 import sqlite3
 
-f = lambda e: 4*e/(np.pi * (3*(1+e) - np.sqrt((3*e+1) * (e+3))))
-
 with sqlite3.connect('glyphs.db') as db:
     general = pd.read_sql_query('select * from pores where lfer > 0.9', db)
 
 shit = pd.read_csv('score.csv')
 data = general.merge(shit, on = 'label', how = 'inner', validate = "1:1")
-
-data['score'] = data['score'] / f(data['elongation'])
 
 normal = data.query('name == "normal/"')
 thin = data.query('name == "thin/"')
@@ -30,6 +26,6 @@ ax.scatter(mnist['convexity'], mnist['elongation'], mnist['score'], marker = '^'
 ax.scatter(mostlyconvex['convexity'], mostlyconvex['elongation'], mostlyconvex['score'], marker = '+')
 ax.set_xlabel('\nConvexity', linespacing = 2)
 ax.set_ylabel('\nElongation', linespacing = 2)
-ax.set_zlabel('Awesomeness')
+ax.set_zlabel('Narrowness')
 ax.legend(['Normal', 'Thin', 'MNIST', 'Mostlyconvex'], markerscale = 2.5)
 plt.savefig('caei.png', bbox_inches = 'tight', pad_inches = 0.4)

### 2024-11-14 scripts/plot-min-max.py

@@ -10,8 +10,6 @@ from PIL.ImageOps import invert
 import sys
 import os
 
-f = lambda e: 4*e/(np.pi * (3*(1+e) - np.sqrt((3*e+1) * (e+3))))
-
 what = sys.argv[1]
 how = sys.argv[2]
 mid = float(sys.argv[3])
@@ -23,7 +21,6 @@ with sqlite3.connect('glyphs.db') as db:
 
 shit = pd.read_csv('score.csv')
 data = general.merge(shit, on = 'label', how = 'inner', validate = "1:1")
-data['score'] = data['score'] / f(data['elongation'])
 
 query = 'convexity >= %f and convexity < %f' % (start, end)
 subdata = data.query(query).sort_values(what, axis = 0)

### 2024-11-14 paper.tex
Awesomeness -> Narrowness + update plots (1/2)
Awesomeness -> Narrowness (2/2)

@@
 Substituting \cref{eq:pre-awesomeness} and \cref{eq:intro} we get a new pore
-shape parameter we call ``\highlight{awesomeness}'':
+shape parameter we call ``narrowness'':
 \begin{equation}
@@
 \label{seq:alg}
-Our algorithm for calculating \highlight{awesomeness} is quite simple. It
-assumes that an image of a pore is made with sufficient resolution, so we can
-use boundary pixels without any additional processing. The main algorithm
-consists of three parts and is shown in \cref{alg:main}.
+Our algorithm for calculating narrowness is quite simple. It assumes that an
+image of a pore is made with sufficient resolution, so we can use boundary
+pixels without any additional processing. The main algorithm consists of three
+parts and is shown in \cref{alg:main}.
 \begin{algorithm}[H]
-  \caption{Algorithm for computation of \highlight{awesomeness} of a pore.}
+  \caption{Algorithm for computation of narrowness of a pore.}
   \label{alg:main}
   \begin{algorithmic}[1]
-    \Procedure{\texttt{awesomeness}}{\texttt{img}}
+    \Procedure{\texttt{narrowness}}{\texttt{img}}
     \State \texttt{bs $\gets$ boundary(img)}
@@
 \begin{algorithm}[H]
-  \caption{The last step of the algorithm for awesomeness: the function \texttt{pmin}.}
+  \caption{The last step of the algorithm for narrowness: the function
+    \texttt{pmin}.}
   \label{alg:pmin}
@@
   \includegraphics[width=0.9\linewidth]{images/rotation-resize.png}
-  \caption[]{\highlight{Awesomeness} parameter for the same image under rotation
-  (red X marks) and resize (blue dot marks) transforms.}
+  \caption[]{Narrowness parameter for the same image under rotation (red X
+    marks) and resize (blue dot marks) transforms.}
   \label{fig:rotation-resize}
@@
 \section{Results}
-We computed \highlight{awesomeness} for 4000 synthetically generated images with
-dimensions $1000 \times 1000$ pixels (1000 images from 4 different
-datasets). The datasets have the following properties:
+We computed narrowness for 4000 synthetically generated images with dimensions
+$1000 \times 1000$ pixels (1000 images from 4 different datasets). The datasets
+have the following properties:
 \begin{itemize}
@@
     \includegraphics[width=0.4\linewidth,frame]{images/mostlyconvex.png}}
-  \caption[]{One pore from each dataset used for calculation of
-    \texttt{awesomeness}.}
+  \caption[]{One pore from each dataset used for calculation of narrowness.}
   \label{fig:pores}
@@
 convexity and elongation parameters. On \cref{fig:cae-space} each pore is
-represented as a dot in convexity-elongation-\highlight{awesomeness} (CEA)
-space.
+represented as a dot in convexity-elongation-narrowness (CEN) space.
 \begin{figure*}
   \centering
-  \subfigure[Convexity-elongation-\highlight{awesomeness} space]{
+  \subfigure[Convexity-elongation-narrowness space]{
     \includegraphics[width=0.4\linewidth]{images/cae.png}
@@
   \vskip\baselineskip
-  \subfigure[Elongation-\highlight{Correlated awesomeness} space]{
+  \subfigure[Elongation-Correlated narrowness space]{
     \includegraphics[width=0.4\linewidth]{images/ae.png}
@@
 
-It can be seen that if a pore has low convexity ($< 0.6$)
-\highlight{awesomeness} adds no information to the pore's descriptors because it
-stays relatively low for all pores. When, however, the convexity is high it adds
-a new dimension to the parameter space.
+It can be seen that if a pore has low convexity ($< 0.6$) narrowness adds no
+information to the pore's descriptors because it stays relatively low for all
+pores. When, however, the convexity is high it adds a new dimension to the
+parameter space.
 
 Another common parameter for describing pore shapes is roundness. Figure
-\ref{fig:cer-space} features convexity-elongation-roundness (CER) space.
-It can be seen that roundness-convexity correlation is bigger than
-awesomeness-convexity correlation. All correlation values are in
-\cref{tab:correlations}.
+\ref{fig:cer-space} features convexity-elongation-roundness (CER) space. It can
+be seen that roundness-convexity correlation is bigger than narrowness-convexity
+correlation. All correlation values are in \cref{tab:correlations}.
 
 On \cref{fig:ae-space} pores are shown in $p-E$ space where $p$ is a
-``correlated'' \highlight{awesomeness} parameter \cref{eq:pre-awesomeness}. It
-shows that our assumption on the maximal value of \highlight{awesomeness} is
-correct indeed.
+``correlated'' narrowness parameter \cref{eq:pre-awesomeness}. It shows that our
+assumption on the maximal value of narrowness is correct indeed.
 
@@
     \hline
-    & Awesomeness & Elongation & Convexity & Roundness \\
+    & Narrowness & Elongation & Convexity & Roundness \\
     \hline
-    Awesomeness & 1 & 0.049 & 0.557 & 0.745 \\
+    Narrowness & 1 & 0.106 & 0.611 & 0.0.800 \\
     \hline
@@
 
-To test abilities of the awesomeness parameter we now divide our pores in groups
-with different convexity. The first group has pores with convexity $0.55 \le C < 0.65$,
-the second -- $0.65 \le C < 0.75$, the third -- $0.75 \le C < 0.85$ and the fourth
--- $0.85 \le C < 0.95$. Five images with the biggest awesomeness and five images
-with the smallest awesomeness from each group are shown on
-\cref{fig:convexity-groups-score}. It can be clearly seen that pores with higher
-values of \highlight{awesomeness} are more ``solid'' and more finely
+To test abilities of the narrowness parameter we now divide our pores in groups
+with different convexity. The first group has pores with convexity
+$0.55 \le C < 0.65$, the second -- $0.65 \le C < 0.75$, the third --
+$0.75 \le C < 0.85$ and the fourth -- $0.85 \le C < 0.95$. Five images with the
+biggest narrowness and five images with the smallest narrowness from each group
+are shown on \cref{fig:convexity-groups-score}. It can be clearly seen that
+pores with higher values of narrowness are more ``solid'' and more finely
 clusterized.
@@
 roundness for convexity $C > 0.8$. For lower convexity, however, even pores with
-the biggest roundness in the group are also underclusterized while
-\highlight{awesomeness} parameter is capable of separating well-clusterized and
-underclusterized pores.
+the biggest roundness in the group are also underclusterized while narrowness
+parameter is capable of separating well-clusterized and underclusterized pores.
 \begin{figure*}
@@
   \caption[]{Pores divided into groups by their convexity. Upper row of each
-    subfigure: pores with minimal \highlight{awesomeness} in the group, lower
-    row: pores with maximal \highlight{awesomeness} in the group.}
+    subfigure: pores with minimal narrowness in the group, lower row: pores with
+    maximal narrowness in the group.}
   \label{fig:convexity-groups-score}
@@
     \hline
-    \highlight{Awesomeness} & Comment \\
+    \highlight{Narrowness} & Comment \\
     \hline
@@
   \end{tabular}
-  \caption{Different values of \highlight{awesomeness} and their meaning.}
+  \caption{Different values of narrowness and their meaning.}
   \label{tab:ranges}
@@
 \item C-shaped pores with a small gap, like the pore on the left-top of
-  \cref{fig:small-gap} always have small \highlight{awesomeness}, even if they
-  are otherwise clusterized correctly.
+  \cref{fig:small-gap} always have small narrowness, even if they are otherwise
+  clusterized correctly.
 \end{itemize}
@@
 increase computational time significantly. We call the parameter $P'$ with
-$d_{AB}$ in the place of $\rho_{AB}$ ``improved awesomeness''. The following
+$d_{AB}$ in the place of $\rho_{AB}$ ``improved narrowness''. The following
 relation always holds: $0 < P \le P' \le 1$.
@@
   \includegraphics[width=0.9\linewidth,frame]{images/improved.png}
-  \caption[]{Pairs of points responsible for \highlight{awesomeness} (red) and
-    improved \highlight{awesomeness} (green).}
+  \caption[]{Pairs of points responsible for narrowness (red) and improved
+    narrowness (green).}
   \label{fig:improved}
@@
 
-We present an opensource solution for calculating \highlight{awesomeness} and
-improved \highlight{awesomeness}. \highlight{E-mail us and buy us coffee so we
-  can send this super program to you, no matter where you live! Hurry, this is a
-limited offer!} An average time for calculating \highlight{awesomeness} is 1
-second for a $1000 \times 1000$ png image and is $1-60$ seconds for calculating
-improved \highlight{awesomeness}.
+We present an opensource solution for calculating narrowness and improved
+narrowness. \highlight{E-mail us and buy us coffee so we can send this super
+  program to you, no matter where you live! Hurry, this is a limited offer!} An
+average time for calculating narrowness is 1 second for a $1000 \times 1000$ png
+image and is $1-60$ seconds for calculating improved narrowness.
 

### 2024-11-14 paper.tex
Add citations

@@
 use conventional functions for working with lists such as \texttt{head},
-\texttt{tail}, \texttt{map}, \texttt{foldl} and so on.
+\texttt{tail}, \texttt{map}, \texttt{foldl} and so on\cite[Chapter~4: Functional
+programming]{o2008real}.
 
@@
 in \cref{eq:intro} with the length $d_{AB}$ of the shortest path between points
-which does not cross the pore's boundary (see \cref{fig:improved}). Although the
-resulting algorithm will have the same $O(n^2)$ complexity, doing so can
-increase computational time significantly. We call the parameter $P'$ with
+which does not cross the pore's boundary (see \cref{fig:improved}). We can treat
+the boundary as a simple polygon and there is a fast $O(n)$ algorithm for
+finding the shortest path between points inside such
+polygon\cite{guibas1986linear} once its triangulation is known. One of the
+simplest triangulation algorithms is ear clipping
+algorithm\cite{eberly2008triangulation} which works in $O(n^2)$ time. Other
+works on the shortest path problem include
+\cite{asano2010constant,har2014shortest,cleve2019experimental,asano1985visibility}.
+Although the resulting algorithm will have the same $O(n^2)$ complexity, doing
+so can increase computational time significantly. We call the parameter $P'$ with
 $d_{AB}$ in the place of $\rho_{AB}$ ``improved narrowness''. The following

### 2024-11-14 paper.tex
Change the title
Add a citation

@@
 
-\title{Look, we can do something}
+\title{Introducing two new parameters for assesing clusterization quality of SEM
+  images}
 
@@
 We present an opensource solution for calculating narrowness and improved
-narrowness. \highlight{E-mail us and buy us coffee so we can send this super
-  program to you, no matter where you live! Hurry, this is a limited offer!} An
-average time for calculating narrowness is 1 second for a $1000 \times 1000$ png
-image and is $1-60$ seconds for calculating improved narrowness.
+narrowness \cite{pore-narrowness}. Average time for calculating narrowness is 1
+second for a $1000 \times 1000$ png image and is $1-60$ seconds for calculating
+improved narrowness.
 
